Wetting of the tarsal adhesive fluid controls underwater adhesion in ladybug beetles

### 2021-05-10 source/tex/ladybug_adhesion.tex
some of edits suggested by Thomas added

\keywords{bio-adhesion; capillary force; bubble; insects; gecko}

@@

While most of the studies on insect adhesion focused on terrestrial species, underwater insect attachment is much more rare and has been relatively unexplored. Some aquatic insects like diving beetles \cite{Chen:2014} or midge larva \cite{Kang:2020} use suction cups to adhere to surfaces. However, underwater adhesion mediated by secreted liquids require the displacement of the water at the interface first and a spreading of the fluid on the substrate. One relatively simple approach is to use an air bubble around the adhesive organs similar to the air bubbles many secondary aquatic insects and spiders carry on their body for breathing underwater \cite{Seymour:2013}. This has been shown in a recent study by \citet{RN87} that that female terrestrial green dock beetles \emph{Gastrophysa viridula} can attach quite well to surfaces underwater by using such an air bubble. Their naturally hydrophobic tarsal hairs trap the bubble around the pads when being submerged underwater, which de-wets the surface on contact. It has been hypothesised that a combination of capillary forces due the air bubble and hair secretions within the de-wetted area results in its adhesion underwater. However, it remains unclear if an air bubble is necessary for adhesion and what, if any, contribution it has to the adhesive force. The oily tarsal adhesive fluid found in insects alone might be sufficient in creating the necessary capillary adhesion even without a bubble, given that the fluid remains on the hair tips when submerged. In ladybug beetles, the tip of each seta secretes approximately one femtoliter of tarsal adhesive fluid by each step \cite{RN108}. The fluid's chemical composition in green dock beetles was identified to be an oil-containing mixture of mostly long chain hydrocarbons\cite{RN96} with traces
of triglycerides, fatty acids and cholesterol in ladybirds \emph{Hemisphaerota cyanea} and \emph{Epilachna vingtipunctuata}\cite{RN221,RN222}, rendering it immiscible with water.

@@

\section{Experimental}

Normal adhesion force measurements on a restrained leg in a live
beetle were performed. We focus our study only on a single tarsal adhesive pad of the leg by carefully fixing it (described later) to prevent any dynamic influence of its claws or other tarsomeres/legs, which might otherwise exist under the beetle's natural walking conditions, influencing its adhesion. 
We characterised adhesion by the pull-off force
during detachment, tested on smooth normal and
fluorinated glass surfaces representing hydrophilic and hydrophobic substrates
respectively. When no water was present, we labelled the mode of contact
as ``\emph{in air}''. Underwater, measurements
were done both in the presence and absence of a trapped air bubble (``\emph{underwater:
bubble}'' and ``\emph{underwater: no bubble}'', respectively) to
investigate the air bubble's role in underwater adhesion. Adhesion force
for each of the labelled contact modes were compared for both substrates.

@@

The seven-spotted adult male adult ladybug beetles (\emph{Coccinella septempuctata})
were purchased from Katz Biotech (Baruth, Germany). The beetles were housed in a plastic box filled with leaves,
twigs and stones at room temperature and 60-80\% relative humidity
with daily access to sunlight. They were fed with raisins, honey and
water \emph{ad libitum}. The beetles on average weighed 34 $\pm$ 4 mg and were experimented on within three weeks of being housed under above conditions.

 %The beetle's leg was constrained similar to the method described by Bullock et al \cite{RN19}.
An individual beetle was first carefully anaesthetised using small amounts of CO\textsubscript{2} sublimating
from a piece of dry ice and then glued with a small dollop of epoxy glue on its elytra to the underside of a heavy steel ball. The ball was held in a bracket which allowed free rotational movement of the ball in each direction, thus helping to align the suspended beetle over the substrate (see Fig.~\ref{fig:Setup}). The bracket with the ball and the beetle could be further positioned by manual micro-manipulators in all three axes before the experiments. One front left leg was carefully fixed at its tibia to a piece of soft solder wire coming off the steel ball using Blu Tack (Bostik Ltd., U.K.), allowing us to further align the leg to the substrate. Each leg of a male ladybug beetle has two hairy adhesive pads. For the test, we only allowed the distal pad to come into contact with the substrate thus minimising partial or bad contact of the other one. The distal pad was thus restrained by fixing its dorsal side to the wire using Blu Tack. The claws on the leg were also fixed to the wire using epoxy glue to prevent any further wiggling and to prevent the claws from touching the substrate (Fig.~\ref{fig:Setup} top-left inset). Care was taken to ensure the glue doesn't contaminate the rest of the tarsomeres. A small piece of non-sticky Teflon tape helped to keep other legs tucked close to the body and avoided any interference during the adhesion test. After the measurements, the beetle was freed by carefully removing the epoxy glue and Blu Tack without harming it and set free.

@@

Five force measurements were subsequently performed, each on a fresh spot of the substrate, and averaged for data analysis. 
Experiments were repeated with five distinct male beetles for each combination of contact mode (``\emph{in air}'', (``\emph{underwater:
bubble}'' and (``\emph{underwater: no bubble}'') and substrate chemistry (hydrophilic and hydrophobic). Thus, in total, 30 distinct beetles were tested. After an experiment, the beetle was marked on its elytra and released back into the box to ensure the same beetle was not used for any subsequent adhesion tests.

@@

For measurements in air, the pull-off force was defined as the minimum
negative force during the retraction step (bottom-right plot in Figure \ref{fig:Setup}).
For underwater measurements, an additional correction was necessary.
When the beetle was partially submerged underwater, its contact line at the
water surface shifted, which influenced the force readout due to surface
tension and buoyancy. This effect needed to be cancelled. So, a ``background''
force data was recorded, where the submerged beetle makes no contact
with the substrate. This background data was then subtracted from
a typical force data with substrate contact to correct for the external
surface tension effects. The pull-off force was subsequently calculated
from the minima as before.

Data sets were compared for statistical differences using pairwise
Student t-test and their corresponding p-value and Common Language
Effect Size (CLES) are reported. Shapiro-Wilk test was done for each
data set to verify a normal distribution of its residuals and Levene's
test was done to check for variance homogeneity, to validate the t-test
assumptions. Bonferroni's correction was used to account for multiple
comparison between groups.

\subsubsection{Substrate preparation}

@@

\begin{figure}[H]
\centering{}\includegraphics[scale=0.5]{Figure2-Expt_effect_of_contact}\caption{\label{fig:Effect-of-contact}Box-and-whisker plot showing
 adhesion force measurements of ladybug beetle's (\emph{Coccinella
septempuctata}) distal pad on normal hydrophilic glass (blue) and hydrophobic PFOTS coated glass (red) substrates in air and underwater
conditions (n=30). The two modes of contact during underwater experiments
are represented separately: \textquotedblleft\emph{bubble}\textquotedblright{}
and \textquotedblleft\emph{no bubble}\textquotedblright . Crosses
represent theoretical predictions (see text) of adhesion force, while, circles
represent the contribution of the bubble itself, calculated from the
capillary bridge model. In the model, hair diameter = 4 \textmu m,
pad diameter = 200 \textmu m, hair length = 40 \textmu m,
N\protect\textsubscript{hairs} = 500, V\protect\textsubscript{fluid}
= 4.2 fL and V\protect\textsubscript{bubble} = 1.2 nL. Interfacial
tension of the tarsal adhesive fluid in air and water were assumed to be
24 mN m\protect\textsuperscript{-1} and 48 mN m\protect\textsuperscript{-1} respectively and water surface tension is 72 mN m\protect\textsuperscript{-1}.}
\end{figure}

Apart from the three depicted contact modes, we observed an additional
fourth mode which occurred in roughly 25\% of our underwater experiments using degassed water.
In this scenario, the ventral view recordings show that none of the hairs
appear to contact well with either glass or PFOTS substrate (supplementary video S5), unlike the other
three contact modes (supplementary video S2-S4). This ``bad contact'' scenario only happened underwater and shows no adhesion 
with either glass or PFOTS substrate. While it was not completely
clear why such a contact occurs, there can be two possible reasons.
First, the hairs could get bundled due to a small air meniscus within
the hairs, resulting in their disorientation. Second, a thin water
layer at the substrate interface might not be drained out to allow
the hairs to make contact with the substrate, resulting in a loss
of adhesion.

@@

A smaller $\hat{V}_{b}$ resulted in increased, but small, attraction
by the bubble on both types of substrates. For larger values of $\hat{V}_{b}$
however, the force trend for the whole pad mostly follows that of
the bubble. This is because the bubble gets big enough to entrap all
the hairs inside it. Thus, the force contribution due to the fluid
bridges remain unchanged, and only the bubble's contribution drives
the slight variation in the pad's adhesion at high $\hat{V}_{b}$.
Once the bubble is small enough such that part of the fluid bridges
start making contact in water, the force trend changes, with a steep
decrease (increase) in adhesion force on hydrophilic (hydrophobic)
substrate as the volume decreases.

\subsection{Adhesion of a hairy pad: Effect of the hair tip diameter}

@@

Predictions of the ladybug's adhesion from the capillary bridge model
agree with our experimental results (Figure \ref{fig:Effect-of-contact}).
In underwater conditions without a trapped air bubble, adhesion to a hydrophobic
substrate is significantly larger than to a hydrophilic substrate.
This is explained by the different interfacial tension of the oily tarsal secretion and its contact
angles with the substrates in air and underwater, which determines
the capillary adhesive force in each case (Figure \ref{fig:Oil-contact-images}).
However, the experiments don't show the predicted $\sim$ 2.6 times
increase in underwater adhesion relative to that in air on the hydrophobic
PFOTS-coated surface. This discrepancy could be due to our assumptions of
the oily fluid's interfacial properties. If we choose $\gamma_{fa}$=30
mN m\protect\textsuperscript{-1} and $\gamma_{fw}$=40 mN m\protect\textsuperscript{-1}, the corresponding increase in adhesion
will be $\sim$ 1.7, closer to our experimental value of $\sim$ 1.
The resulting change in $\theta_{fa}$ and $\theta_{fw}$ will further
decrease this number. Direct measurement of the fluid's interfacial
properties is thus essential to better predict the insect's adhesion,
and will be a subject of future studies. Further, due to surface inhomogeneities,
not all the hairs might be able to completely drain the interfacial
water layer, in order for the tarsal adhesive fluid to make a direct contact
with the substrate. This can further reduce underwater adhesion, in
comparison to our theoretical predictions which assumes a perfect
contact of all hairs' terminals.

In the model, we assume that all the hairs detach simultaneously to
give a theoretical maximum achievable adhesion force. In our experiments,
however, not all hairs make a perfect contact with the substrate despite our 
best efforts to align the pad parallel to the surface. Furthermore, during detachment, 
the constrained pad typically peels off from its proximal to distal end rather
than detach simultaneously. Our model also assumes the hairs to be
of similar geometry, unlike the male beetle's pad which has a distribution
of flat or pointed tipped hairs. Thus, it's not surprising that the
model overestimates the adhesion forces. The predictions are however
in the same order of magnitude as experiments, and the qualitative
trend is consistent for both hydrophilic and hydrophobic substrates
in air and underwater.

>>>>

\keywords{bio-adhesion; capillary force; air plastron; insects; gecko}

@@

While most of the studies on insect adhesion focused on terrestrial species, underwater insect attachment is much more rare and has been relatively unexplored. Some aquatic insects like diving beetles \cite{Chen:2014} or midge larva \cite{Kang:2020} use suction cups to adhere to surfaces. However, underwater adhesion mediated by secreted liquids require the displacement of the water at the interface first and a spreading of the fluid on the substrate. One relatively simple approach is to use an air bubble around the adhesive organs similar to the air bubbles many secondary aquatic insects and spiders carry on their body for breathing underwater \cite{Seymour:2013}. This has been shown in a recent study by \citet{RN87} that that female terrestrial green dock beetles \emph{Gastrophysa viridula} can attach quite well to surfaces underwater by using such an air bubble. Their naturally hydrophobic tarsal hairs trap the bubble around the pads when being submerged underwater, which de-wets the surface on contact. It has been hypothesised that a combination of capillary forces due the air bubble and hair secretions within the de-wetted area results in its adhesion underwater. However, it remains unclear if an air bubble is necessary for adhesion and what, if any, contribution it has to the adhesive force. The oily tarsal adhesive fluid found in insects alone might be sufficient in creating the necessary capillary adhesion even without a bubble, given that the fluid remains on the hair tips when submerged. In ladybug beetles, the tip of each seta secretes approximately one femtoliter of tarsal adhesive fluid by each step \cite{RN108}. The fluid's chemical composition in green dock beetles was identified to be an oil-containing mixture of mostly long chain hydrocarbons\cite{RN96} with traces
of triglycerides, fatty acids and cholesterol in ladybirds \emph{Hemisphaerota cyanea} and \emph{Epilachna vingtipunctuata}\cite{RN221,RN222}, rendering it immiscible with water. %split references%

@@

\section{Experimental}
%normal to untrated glass%
Normal adhesion force measurements on a restrained leg in a live
beetle were performed. We focused our study only on a single tarsal adhesive pad of the leg by carefully immobilizing it (described later) to prevent any dynamic influence of its claws or other tarsomeres/legs, which might otherwise exist under the beetle's natural walking conditions, influencing its adhesion. 
We characterised adhesion by the pull-off force
during detachment, tested on smooth normal and
fluorinated glass surfaces representing hydrophilic and hydrophobic substrates
respectively. When no water was present, we labelled the mode of contact
as ``\emph{in air}''. Underwater, measurements
were done both in the presence and absence of a trapped air bubble (``\emph{underwater:
bubble}'' and ``\emph{underwater: no bubble}'', respectively) to
investigate the air bubble's role in underwater adhesion. Adhesion force
for each of the labelled contact modes were compared for both substrates.

@@

The adult seven-spotted male ladybug beetles (\emph{Coccinella septempuctata})
were purchased from Katz Biotech (Baruth, Germany). The beetles were housed in a plastic box filled with leaves,
twigs and stones at room temperature and 60-80\% relative humidity
with natural daylight. They were fed with raisins, honey and
water \emph{ad libitum}. The beetles on average weighed 34 $\pm$ 4 mg and were used within three weeks of being housed under above conditions.

 %The beetle's leg was constrained similar to the method described by Bullock et al \cite{RN19}.
An individual beetle was first carefully anaesthetised using small amounts of CO\textsubscript{2} sublimating
from a piece of dry ice and then glued with a small dollop of epoxy glue on its elytra to the underside of a heavy steel ball. The ball was held in a bracket which allowed free rotational movement of the ball in each direction, thus helping to align the suspended beetle over the substrate (see Fig.~\ref{fig:Setup}). The bracket with the ball and the beetle could be further positioned by manual micro-manipulators in all three axes before the experiments. One front left leg was carefully fixed at its tibia to a piece of soft solder wire coming off the steel ball using Blu Tack (Bostik Ltd., U.K.), allowing us to further align the leg to the substrate. Each leg of a male ladybug beetle has two hairy adhesive pads. For the test, we only allowed the distal pad to come into contact with the substrate thus minimising partial or bad contact of the other one. The distal pad was thus restrained by fixing its dorsal side to the wire using Blu Tack. The claws on the leg were also fixed to the wire using epoxy glue to prevent any further movement and to prevent the claws from touching the substrate (Fig.~\ref{fig:Setup} top-left inset). Care was taken to ensure the glue doesn't contaminate the rest of the tarsomeres. A small piece of non-sticky Teflon tape helped to keep other legs tucked close to the body and avoided any interference during the adhesion test. After the measurements, the beetle was freed by carefully removing the epoxy glue and Blu Tack without harming it and set free.

@@

Five force measurements were subsequently performed, each on a fresh spot of the substrate, and averaged for data analysis. 
Experiments were repeated with five distinct male beetles for each combination of contact mode (``\emph{in air}'', ``\emph{underwater:
bubble}'' and ``\emph{underwater: no bubble}'') and substrate chemistry (hydrophilic and hydrophobic). Thus, in total, 30 distinct beetles were tested. After an experiment, the beetle was marked on its elytra and released back into the box to ensure the same beetle was not used for any subsequent adhesion tests.
%mention data points number clearly for each box, what is averaged etc. also%

@@

For measurements in air, the pull-off force was defined as the minimum
negative force during the retraction step (bottom-right plot in Figure \ref{fig:Setup}).
For underwater measurements, an additional correction was necessary.
When the beetle was partially submerged underwater, its contact line at the
water surface shifted, which influenced the force readout due to surface
tension and buoyancy. This effect needed to be cancelled. Therefore, a ``background''
force data was recorded, where the submerged beetle makes no contact
with the substrate. This background data was then subtracted from
a typical force data with substrate contact to correct for the external
surface tension effects. The pull-off force was subsequently calculated
from the minima as before.

Data sets were compared for statistical differences using pairwise
Student t-test and their corresponding p-value and Common Language
Effect Size (CLES) are reported. Shapiro-Wilk test was done for each
data set to verify a normal distribution of its residuals and Levene's
test was done to check for variance homogeneity, to validate the t-test
assumptions. Bonferroni's correction was used to account for multiple
comparison between groups.
%Include ANOVA as well, include F, t, degrees of freedom%
\subsubsection{Substrate preparation}

@@

\begin{figure}[H]
\centering{}\includegraphics[scale=0.5]{Figure2-Expt_effect_of_contact}\caption{\label{fig:Effect-of-contact}Box-and-whisker plot showing
 adhesion force measurements of ladybug beetle's (\emph{Coccinella
septempuctata}) distal pad on normal hydrophilic glass (blue) and hydrophobic PFOTS coated glass (red) substrates in air and underwater
conditions (n=30). The two modes of contact during underwater experiments
are represented separately: \textquotedblleft\emph{bubble}\textquotedblright{}
and \textquotedblleft\emph{no bubble}\textquotedblright . Crosses
represent theoretical predictions (see text) of adhesion force, while, circles
represent the contribution of the bubble itself, calculated from the
capillary bridge model. In the model, hair diameter = 4 \textmu m,
pad diameter = 200 \textmu m, hair length = 40 \textmu m,
N\protect\textsubscript{hairs} = 500, V\protect\textsubscript{fluid}
= 4.2 fL and V\protect\textsubscript{bubble} = 1.2 nL. Interfacial
tension of the tarsal adhesive fluid in air and water were assumed to be
24 mN m\protect\textsuperscript{-1} and 48 mN m\protect\textsuperscript{-1} respectively and water surface tension is 72 mN m\protect\textsuperscript{-1}.}
\end{figure}
%outlier%
Apart from the three depicted contact modes, we observed an additional
fourth mode which occurred in roughly 25\% of our underwater experiments using degassed water.
In this scenario, the ventral view recordings show that none of the hairs
appear to contact well with either glass or PFOTS substrate (supplementary video S5), unlike the other
three contact modes (supplementary video S2-S4). This ``bad contact'' scenario only happened underwater and shows no adhesion 
with either glass or PFOTS substrate. While it was not completely
clear why such a contact occurs, there can be two possible reasons.
First, the hairs could get bundled due to a small air meniscus within
the hairs, resulting in their disorientation. Second, a thin water
layer at the substrate interface might not be drained out to allow
the hairs to make contact with the substrate, resulting in a loss
of adhesion.

@@

A smaller $\hat{V}_{b}$ resulted in increased, but small, attraction
by the bubble on both types of substrates. For larger values of $\hat{V}_{b}$
however, the force trend for the whole pad mostly follows that of
the bubble. This is because the bubble gets big enough to entrap all
the hairs inside it. Thus, the force contribution due to the fluid
bridges remain unchanged, and only the bubble's contribution drives
the slight variation in the pad's adhesion at high $\hat{V}_{b}$.
Once the bubble is small enough such that part of the fluid bridges
start making contact in water, the force trend changes, with a steep
decrease (increase) in adhesion force on hydrophilic (hydrophobic)
substrate as the volume decreases.
%change 1e6 to 1 10^6%
\subsection{Adhesion of a hairy pad: Effect of the hair tip diameter}

@@

Predictions of the ladybug's adhesion from the capillary bridge model
agree with our experimental results (Figure \ref{fig:Effect-of-contact}).
In underwater conditions without a trapped air bubble, adhesion to a hydrophobic
substrate is significantly larger than to a hydrophilic substrate.
This is explained by the different interfacial tension of the oily tarsal secretion and its contact
angles with the substrates in air and underwater, which determines
the capillary adhesive force in each case (Figure \ref{fig:Oil-contact-images}).
However, the experiments don't show the predicted $\sim$ 2.6 times
increase in underwater adhesion relative to that in air on the hydrophobic
PFOTS-coated surface. This discrepancy could be due to our assumptions of
the oily fluid's interfacial properties. If we choose $\gamma_{fa}$=30
mN m\protect\textsuperscript{-1} and $\gamma_{fw}$=40 mN m\protect\textsuperscript{-1}, the corresponding increase in adhesion
will be $\sim$ 1.7, closer to our experimental value of $\sim$ 1.
The resulting change in $\theta_{fa}$ and $\theta_{fw}$ will further
decrease this number. Direct measurement of the fluid's interfacial
properties is thus essential to better predict the insect's adhesion,
and will be a subject of future studies. Further, due to surface inhomogeneities,
not all the hairs might be able to completely drain the interfacial
water layer, in order for the tarsal adhesive fluid to make a direct contact
with the substrate. This can further reduce underwater adhesion, in
comparison to our theoretical predictions which assumes a perfect
contact of all hairs' terminals.
%FDMS keep as unpublished data, remove from supplementary.%
In the model, we assume that all the hairs detach simultaneously to
give a theoretical maximum achievable adhesion force. In our experiments,
however, not all hairs make a perfect contact with the substrate despite our 
best efforts to align the pad parallel to the surface. Furthermore, during detachment, 
the constrained pad typically peels off from its proximal to distal end rather
than detach simultaneously. Our model also assumes the hairs to be
of similar geometry, unlike the male beetle's pad which has a distribution
of flat or pointed tipped hairs. Thus, it's not surprising that the
model overestimates the adhesion forces. The predictions are however
in the same order of magnitude as experiments, and the qualitative
trend is consistent for both hydrophilic and hydrophobic substrates
in air and underwater.
